Web-based Supplementary Materials for Combinatorial Mixture Models for Single-Cell Assays with Application to Vaccine Studies by Greg Finak, Steve De Rosa, Mario Roederer and Raphael Gottardo

### 2012-07-30 WebSupplementaryMaterialMIMOSA.tex
multivariate mcmc described
Signed-off-by: Greg Finak <gfinak@fhcrc.org>

\noindent\textbf{MCMC algorithm}\\
In what follows, we use $(x|y)$ to denote the conditional distribution of $x$ given $y$. In particular, we use $(x|\cdots)$ to denote the distribution of $x$ conditional on everything else in the model. Our MCMC algorithms cycle through the following steps: 
\begin{enumerate}
\item Update each $\alpha_u, \beta_u, \alpha_s$ and $\beta_s$ by Metropolis-Hastings using a Gaussian symmetric proposal where the variance of the proposal is tuned for each parameter using the approach of~\cite{Gelman:2004tc,Raftery:1992vp,Raftery:1996ws}.
\item Update $w$ by Gibbs sampling using the full conditional,
\[
(w|\cdots)\sim \mathrm{Beta}(\sum_i z_i,\sum_i (1-z_i))
\]
\item for each $i$, update $z_i$ by Gibbs sampling using the following full conditional,
\[
(z_i|\cdots)\sim\mathrm{B(1,p_i)}
\]
where,
\[
p_i=\frac{w\cdot\mathrm{L_1}}{w\cdot\mathrm{L_1}+(1-w)\cdot\mathrm{L_0}}
\]
\end{enumerate}
For each updated parameter, step 1 above involves the calculation of the following acceptance ratio, with the example below given for $\alpha_u$,
\[
\begin{split}
\frac{\mathrm{L_0}(\alpha^{\text{new}}_u|\cdots)\mathrm{L_1}(\alpha^{\text{new}}_u|\cdots)\pi(\alpha^{\text{new}}_u)}{\mathrm{L_0}(\alpha^{\text{old}}_u|\cdots)\mathrm{L_1}(\alpha^{\text{old}}_u|\cdots)\pi(\alpha^{\text{old}}_u)}\\
\end{split}
\]
where $\pi$ is the prior distribution of $\alpha_u$. The obvious changes in the above expression are made for the acceptance ratios of $\alpha_s,\beta_s,\beta_0$. In our case each parameter has the same exponential prior with mean $1,000$
\subsection{Constrained beta--binomial model}
\label{supp:constrained}
We can define a model where we constrain the stimulated proportions under the alternative model such that $p_s>p_u$. In this case, the only changes required are for the alternative marginal likelihood $\mathrm{L}_1$ defined in the main manuscript by (1). Due to the constraint, the normalizing constant of the prior under the alternative (model ${\cal M}_1$) is not given by $\mathrm{B}(\alpha_u,\beta_u)\mathrm{B}(\alpha_s,\beta_s)$ but requires computing \[
Z(\alpha_u, \beta_u, \alpha_s, \beta_s)=\int_{0}^1{p_u}^{\alpha_u-1}(1-p_u)^{\beta_u-1}\int_{p_u}^1 p_s^{\alpha_s-1}(1-p_s)^{\beta_s-1}dp_sdp_u.
\]
Using this expression, the constrained alternative marginal likelihood can be written as 
\begin{align}
	\begin{split}
\mathrm{L}_1(\alpha_u,\beta_u,\alpha_s,\beta_s|\mathbf{y}) 
=&\prod_{i=1}^P\binom{N_{ui}}{n_{ui}} \binom{N_{si}}{n_{si}}\cdot\\ &\frac{Z(n_{ui}+\alpha_u,N_{ui}-n_{ui}+\beta_u,n_{si}+\alpha_s,N_{si}-n_{si}+\beta_s)}{Z(\alpha_u,\beta_u,\alpha_s,\beta_s)}.\\
\label{model2:constrained}
\end{split}
\end{align}

@@

\[
\begin{split}
Pr(\mathbf{n}_s,\mathbf{n}_u|\boldsymbol{\alpha}_u)=&\int_0^1Pr(\mathbf{n}_s,\mathbf{n}_u|\boldsymbol{\alpha}_u,\mathbf{p}_u)Pr(\mathbf{p}_u|\boldsymbol{\alpha}_u)\mathrm{d}\mathbf{p}_u\\
=&\int_0^1Pr(\mathbf{n}_s|\boldsymbol{\alpha}_u,\mathbf{p}_u)Pr(\mathbf{n}_u|\boldsymbol{\alpha}_u,\mathbf{p}_u)Pr(\mathbf{p}_u|\boldsymbol{\alpha}_u)\mathrm{d}\mathbf{p}_u\\
=&\int_0^1 \mathcal{M}(\mathbf{N}_u,\mathbf{p}_u)\mathcal{M}(\mathbf{N}_s,\mathbf{p}_u)\mathrm{Dir}(\boldsymbol{\alpha}_u)\mathrm{d}\mathbf{p}_u\\
=&\int_0^1 \frac{\mathbf{N}_s!}{\prod_k \mathbf{n}_{sk}!}\prod_k p^{n_{sk}}_{uk} \frac{\mathbf{N}_u!}{\prod_k \mathbf{n}_{uk}!}\prod_k p^{n_{uk}}_{uk}\frac{1}{\mathrm{B}(\boldsymbol{\alpha}_u)}\prod_k p_{uk}^{\alpha_{uk}-1}\mathrm{d}\mathbf{p}_u\\
=&\frac{\mathbf{N}_s!}{\prod_k \mathbf{n}_{sk}!}\frac{\mathbf{N}_u!}{\prod_k \mathbf{n}_{uk}!}\frac{1}{\mathrm{B}(\boldsymbol{\alpha}_u)}\int_0^1 \prod_k p^{n_{sk}+n_{uk}+\alpha_{uk}-1}_{uk}\mathrm{d}\mathbf{p}_u\\
=&\frac{\mathbf{N}_s!}{\prod_k \mathbf{n}_{sk}!}\frac{\mathbf{N}_u!}{\prod_k \mathbf{n}_{uk}!}\frac{\mathrm{B}(\mathbf{n}_s+\mathbf{n}_u+\boldsymbol{\alpha}_u)}{\mathrm{B}(\boldsymbol{\alpha}_u)}
\end{split}
\]
The product over all observations gives the marginal likelihood,
\[
\mathrm{L_0}(\boldsymbol{\alpha}_u|\mathbf{n}_s,\mathbf{n}_u)=\prod_{i=0}^P \frac{\mathbf{N}_{si}!}{\prod_k \mathbf{n}_{sik}!}\frac{\mathbf{N}_{ui}!}{\prod_k \mathbf{n}_{uik}!}\frac{\mathrm{B}(\mathbf{n}_{si}+\mathbf{n}_{ui}+\boldsymbol{\alpha}_{u})}{\mathrm{B}(\boldsymbol{\alpha}_{u})}
\]

For the responder component, again the $\mathbf{n}_s$ are drawn from an independent multinomial distribution, and the $\mathbf{p}_s$ from a dirichlet with hyperparameters $\boldsymbol{\alpha_s}$, giving,
\[
\begin{split}
Pr(\mathbf{n}_s,\mathbf{n}_u|\boldsymbol{\alpha}_u,\boldsymbol{\alpha}_s)=&\int_0^1\int_0^1 \mathcal{M}(\mathbf{N}_u,\mathbf{p}_u)\mathcal{M}(\mathbf{N}_s,\mathbf{p}_s)\mathrm{Dir}(\boldsymbol{\alpha}_u)\mathrm{Dir}(\boldsymbol{\alpha}_s)\mathrm{d}\mathbf{p}_u\mathrm{d}\mathbf{p}_s\\
=&\frac{\mathbf{N}_s!}{\prod_k \mathbf{n}_{sk}!}\frac{\mathbf{N}_u!}{\prod_k \mathbf{n}_{uk}!}\frac{1}{\mathrm{B}(\boldsymbol{\alpha}_u)\mathrm{B}(\boldsymbol{\alpha}_s)}\int_0^1\prod_k p^{n_{uk}+\alpha_{uk}-1}_{uk}\int_0^1 \prod_k p^{n_{sk}+\alpha_{sk}-1}_{sk}\mathrm{d}\mathbf{p}_u\mathrm{d}\mathbf{p}_s\\
=&\frac{\mathbf{N}_s!}{\prod_k \mathbf{n}_{sk}!}\frac{\mathbf{N}_u!}{\prod_k \mathbf{n}_{uk}!}\frac{\mathrm{B}(\mathbf{n}_u+\boldsymbol{\alpha}_u)\mathrm{B}(\mathbf{n}_s+\boldsymbol{\alpha}_s)}{\mathrm{B}(\boldsymbol{\alpha}_u)\mathrm{B}(\boldsymbol{\alpha}_s)}
\end{split}
\]
with marginal likelihood:
\[
\mathrm{L_1}(\boldsymbol{\alpha}_s,\boldsymbol{\alpha}_u|\mathbf{n}_s,\mathbf{n}_u)=\prod_{i=0}^P\frac{\mathbf{N}_{si}!}{\prod_k \mathbf{n}_{sik}!}\frac{\mathbf{N}_{ui}!}{\prod_k \mathbf{n}_{uik}!}\frac{\mathrm{B}(\mathbf{n}_{ui}+\boldsymbol{\alpha}_u)\mathrm{B}(\mathbf{n}_{si}+\boldsymbol{\alpha}_s)}{\mathrm{B}(\boldsymbol{\alpha}_u)\mathrm{B}(\boldsymbol{\alpha}_s)}
\]
\noindent\textbf{MCMC algorithm}\\
GREG: Look at the what I did above, and do something similar here.
\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
%   \includegraphics[width=.75\columnwidth]{Figures/2}\\ 
%   \includegraphics[width=.75\columnwidth]{Figures/12} 
\begin{tikzpicture} [auto, node distance=0cm]
 \node at (0,) (A) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=.5\columnwidth]{Figures/3}};
        \begin{scope}[x={(b.south east)},y={(b.north west)}]
        \node at (0,1) [font=\small\sffamily] {A} ;
                \end{scope}
        \end{tikzpicture}
 };
 \node [right=of A] (B) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (c) {\includegraphics[width=.5\columnwidth]{Figures/5}};
        \begin{scope}[x={(c.south east)},y={(c.north west)}]
        \node at (0,1) [font=\small\sffamily] {B} ;
        \end{scope}
        \end{tikzpicture}
};
\node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=.5\columnwidth]{Figures/6}};
        \begin{scope}[x={(d.south east)},y={(d.north west)}]
        \node at (0,1) [font=\small\sffamily] {C} ;
                \end{scope}
        \end{tikzpicture}
};
\node [right=of C] (D) {
\begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (e) {\includegraphics[width=.5\columnwidth]{Figures/7}};
        \begin{scope}[x={(d.south east)},y={(d.north west)}]
        \node at (0,1) [font=\small\sffamily] {D} ;
                \end{scope}
        \end{tikzpicture}
 };
   % \node[anchor=south west, inner sep=0] at (8,-7.5){\includegraphics[width=.5\columnwidth]{Figures/8}};
   % \node[anchor=south west, inner sep=0] at (0,-11.25){\includegraphics[width=.5\columnwidth]{Figures/9}};
    %\node[anchor=south west, inner sep=0] at (8,-11.25){\includegraphics[width=.5\columnwidth]{Figures/10}};
    %\node[anchor=south west, inner sep=0] at (0,-15){\includegraphics[width=.5\columnwidth]{Figures/11}};
    %\node[anchor=south west, inner sep=0] at (8,-15){\includegraphics[width=.5\columnwidth]{Figures/13}};

>>>>

\noindent\textbf{MCMC algorithm}\\
In what follows, we use $(x|y)$ to denote the conditional distribution of $x$ given $y$. In particular, we use $(x|\cdots)$ to denote the distribution of $x$ conditional on everything else in the model. Our MCMC algorithms cycle through the following steps: 
\begin{enumerate}
\item Update each $\alpha_u, \beta_u, \alpha_s$ and $\beta_s$ by Metropolis-Hastings using a Gaussian symmetric proposal where the variance of the proposal is tuned for each parameter using the approach of~\cite{Gelman:2004tc,Raftery:1992vp,Raftery:1996ws}.
\item Update $w$ by Gibbs sampling using the full conditional,
\[
(w|\cdots)\sim \mathrm{Beta}(\sum_i z_i,\sum_i (1-z_i))
\]
\item for each $i$, update $z_i$ by Gibbs sampling using the following full conditional,
\[
(z_i|\cdots)\sim\mathrm{B(1,p_i)}
\]
where,
\[
p_i=\frac{w\cdot\mathrm{L_1}}{w\cdot\mathrm{L_1}+(1-w)\cdot\mathrm{L_0}}
\]
\end{enumerate}
For each updated parameter, step 1 above involves the calculation of the following acceptance ratio, (e.g. $\alpha_u$, below),
\[
\begin{split}
\frac{\mathrm{L_0}(\alpha^{\text{new}}_u|\cdots)\mathrm{L_1}(\alpha^{\text{new}}_u|\cdots)\pi(\alpha^{\text{new}}_u)}{\mathrm{L_0}(\alpha^{\text{old}}_u|\cdots)\mathrm{L_1}(\alpha^{\text{old}}_u|\cdots)\pi(\alpha^{\text{old}}_u)}\\
\end{split}
\]
where $\pi$ is the prior distribution of $\alpha_u$. The obvious changes in the above expression are made for the acceptance ratios of $\alpha_s,\beta_s,\beta_0$. In our case each parameter has the same exponential prior with mean $1,000$
\subsection{Constrained beta--binomial model}
\label{supp:constrained}
We can define a model where we constrain the stimulated proportions under the alternative model such that $p_s>p_u$. In this case, the only changes required are for the alternative marginal likelihood $\mathrm{L}_1$ defined in the main manuscript by (1). Due to the constraint, the normalizing constant of the prior under the alternative (model ${\cal M}_1$) is not given by $\mathrm{B}(\alpha_u,\beta_u)\mathrm{B}(\alpha_s,\beta_s)$ but requires computing \[
Z(\alpha_u, \beta_u, \alpha_s, \beta_s)=\int_{0}^1{p_u}^{\alpha_u-1}(1-p_u)^{\beta_u-1}\int_{p_u}^1 p_s^{\alpha_s-1}(1-p_s)^{\beta_s-1}dp_sdp_u.
\]
Using this expression, the constrained alternative marginal likelihood can be written as 
\begin{align}
	\begin{split}
\mathrm{L}_1(\alpha_u,\beta_u,\alpha_s,\beta_s|\mathbf{y}) 
=&\prod_{i=1}^P\binom{N_{ui}}{n_{ui}} \binom{N_{si}}{n_{si}}\cdot\\ &\frac{Z(n_{ui}+\alpha_u,N_{ui}-n_{ui}+\beta_u,n_{si}+\alpha_s,N_{si}-n_{si}+\beta_s)}{Z(\alpha_u,\beta_u,\alpha_s,\beta_s)}.\\
\label{model2:constrained}
\end{split}
\end{align}

@@

\[
\begin{split}
Pr(\mathbf{n}_s,\mathbf{n}_u|\boldsymbol{\alpha}_u)=&\int_0^1Pr(\mathbf{n}_s,\mathbf{n}_u|\boldsymbol{\alpha}_u,\mathbf{p}_u)Pr(\mathbf{p}_u|\boldsymbol{\alpha}_u)\mathrm{d}\mathbf{p}_u\\
=&\int_0^1Pr(\mathbf{n}_s|\boldsymbol{\alpha}_u,\mathbf{p}_u)Pr(\mathbf{n}_u|\boldsymbol{\alpha}_u,\mathbf{p}_u)Pr(\mathbf{p}_u|\boldsymbol{\alpha}_u)\mathrm{d}\mathbf{p}_u\\
=&\int_0^1 \mathcal{M}(\mathbf{N}_u,\mathbf{p}_u)\mathcal{M}(\mathbf{N}_s,\mathbf{p}_u)\mathrm{Dir}(\boldsymbol{\alpha}_u)\mathrm{d}\mathbf{p}_u\\
=&\int_0^1 \frac{\mathbf{N}_s!}{\prod_k \mathbf{n}_{sk}!}\prod_k p^{n_{sk}}_{uk} \frac{\mathbf{N}_u!}{\prod_k \mathbf{n}_{uk}!}\prod_k p^{n_{uk}}_{uk}\frac{1}{\mathrm{B}(\boldsymbol{\alpha}_u)}\prod_k p_{uk}^{\alpha_{uk}-1}\mathrm{d}\mathbf{p}_u\\
=&\frac{\mathbf{N}_s!}{\prod_k \mathbf{n}_{sk}!}\frac{\mathbf{N}_u!}{\prod_k \mathbf{n}_{uk}!}\frac{1}{\mathrm{B}(\boldsymbol{\alpha}_u)}\int_0^1 \prod_k p^{n_{sk}+n_{uk}+\alpha_{uk}-1}_{uk}\mathrm{d}\mathbf{p}_u\\
=&\frac{\mathbf{N}_s!}{\prod_k \mathbf{n}_{sk}!}\frac{\mathbf{N}_u!}{\prod_k \mathbf{n}_{uk}!}\frac{\mathrm{B}(\mathbf{n}_s+\mathbf{n}_u+\boldsymbol{\alpha}_u)}{\mathrm{B}(\boldsymbol{\alpha}_u)}
\end{split}
\]
The product over all $P$ observations gives the marginal likelihood,
\[
\mathrm{L_0}(\boldsymbol{\alpha}_u|\mathbf{n}_s,\mathbf{n}_u)=\prod_{i=0}^P \frac{\mathbf{N}_{si}!}{\prod_k \mathbf{n}_{sik}!}\frac{\mathbf{N}_{ui}!}{\prod_k \mathbf{n}_{uik}!}\frac{\mathrm{B}(\mathbf{n}_{si}+\mathbf{n}_{ui}+\boldsymbol{\alpha}_{u})}{\mathrm{B}(\boldsymbol{\alpha}_{u})}
\]

For the responder component, again the $\mathbf{n}_s$ are drawn from an independent multinomial distribution, and the $\mathbf{p}_s$ from a dirichlet with hyperparameters $\boldsymbol{\alpha_s}$, giving,
\[
\begin{split}
Pr(\mathbf{n}_s,\mathbf{n}_u|\boldsymbol{\alpha}_u,\boldsymbol{\alpha}_s)=&\int_0^1\int_0^1 \mathcal{M}(\mathbf{N}_u,\mathbf{p}_u)\mathcal{M}(\mathbf{N}_s,\mathbf{p}_s)\mathrm{Dir}(\boldsymbol{\alpha}_u)\mathrm{Dir}(\boldsymbol{\alpha}_s)\mathrm{d}\mathbf{p}_u\mathrm{d}\mathbf{p}_s\\
=&\frac{\mathbf{N}_s!}{\prod_k \mathbf{n}_{sk}!}\frac{\mathbf{N}_u!}{\prod_k \mathbf{n}_{uk}!}\frac{1}{\mathrm{B}(\boldsymbol{\alpha}_u)\mathrm{B}(\boldsymbol{\alpha}_s)}\int_0^1\prod_k p^{n_{uk}+\alpha_{uk}-1}_{uk}\int_0^1 \prod_k p^{n_{sk}+\alpha_{sk}-1}_{sk}\mathrm{d}\mathbf{p}_u\mathrm{d}\mathbf{p}_s\\
=&\frac{\mathbf{N}_s!}{\prod_k \mathbf{n}_{sk}!}\frac{\mathbf{N}_u!}{\prod_k \mathbf{n}_{uk}!}\frac{\mathrm{B}(\mathbf{n}_u+\boldsymbol{\alpha}_u)\mathrm{B}(\mathbf{n}_s+\boldsymbol{\alpha}_s)}{\mathrm{B}(\boldsymbol{\alpha}_u)\mathrm{B}(\boldsymbol{\alpha}_s)}
\end{split}
\]
with marginal likelihood:
\[
\mathrm{L_1}(\boldsymbol{\alpha}_s,\boldsymbol{\alpha}_u|\mathbf{n}_s,\mathbf{n}_u)=\prod_{i=0}^P\frac{\mathbf{N}_{si}!}{\prod_k \mathbf{n}_{sik}!}\frac{\mathbf{N}_{ui}!}{\prod_k \mathbf{n}_{uik}!}\frac{\mathrm{B}(\mathbf{n}_{ui}+\boldsymbol{\alpha}_u)\mathrm{B}(\mathbf{n}_{si}+\boldsymbol{\alpha}_s)}{\mathrm{B}(\boldsymbol{\alpha}_u)\mathrm{B}(\boldsymbol{\alpha}_s)}
\]
\noindent\textbf{MCMC algorithm}\\
The MCMC algorithm for the dirichlet--multinomial model is analogous to the beta--binomial, above. The parameter vectors $\boldsymbol{\alpha}_s,\boldsymbol{\alpha}_u$ are updated component--wise:
\begin{enumerate}
\item  Update each $\alpha_{sk}$, $\alpha_{uk}$ using a Gaussian symmetric proposal distribution with the variance of each proposal tuned using the approach of~\cite{Gelman:2004tc}. 
\item Update $w$ by Gibbs sampling using the full conditional,
\[
(w|\cdots)\sim\mathrm{Beta}(\sum_i z_i,\sum_i(1-z_i))
\]
\item For each $i$, update $z_i$ using the full conditional,
\[
(z_i|\cdots)\sim \mathrm{B}(1,p_i)
\]
where 
\[
p_i = \frac{w\cdot\mathrm{L_1}}{w\cdot\mathrm{L_1}+(1-w)\cdot\mathrm{L_0}}
\]
For each parameter component updated in step 1 above, compute the acceptance ratio (e.g. $\alpha_{uk}$, below):
\[
\frac{\mathrm{L_0}(\alpha^{\text{new}}_{uk}|\cdots)\mathrm{L_1}(\alpha^{\text{new}}_{uk}|\cdots)\pi(\alpha^{\text{new}}_{uk})}{\mathrm{L_0}(\alpha^{\text{old}}_{uk}|\cdots)\mathrm{L_1}(\alpha^{\text{old}}_{uk}|\cdots)\pi(\alpha^{\text{old}}_{uk})}\\
\]

where $\pi$ is the prior distribution of the parameter. Again, we have used the same exponential prior with mean 1,000 for each parameter.
\end{enumerate}

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
%   \includegraphics[width=.75\columnwidth]{Figures/2}\\ 
%   \includegraphics[width=.75\columnwidth]{Figures/12} 
\begin{tikzpicture} [auto, node distance=0cm]
 \node at (0,) (A) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=.5\columnwidth]{Figures/3}};
        \begin{scope}[x={(b.south east)},y={(b.north west)}]
        \node at (0,1) [font=\small\sffamily] {A} ;
                \end{scope}
        \end{tikzpicture}
 };
 \node [right=of A] (B) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (c) {\includegraphics[width=.5\columnwidth]{Figures/5}};
        \begin{scope}[x={(c.south east)},y={(c.north west)}]
        \node at (0,1) [font=\small\sffamily] {B} ;
        \end{scope}
        \end{tikzpicture}
};
\node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=.5\columnwidth]{Figures/6}};
        \begin{scope}[x={(d.south east)},y={(d.north west)}]
        \node at (0,1) [font=\small\sffamily] {C} ;
                \end{scope}
        \end{tikzpicture}
};
\node [right=of C] (D) {
\begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (e) {\includegraphics[width=.5\columnwidth]{Figures/7}};
        \begin{scope}[x={(d.south east)},y={(d.north west)}]
        \node at (0,1) [font=\small\sffamily] {D} ;
                \end{scope}
        \end{tikzpicture}
 };
   % \node[anchor=south west, inner sep=0] at (8,-7.5){\includegraphics[width=.5\columnwidth]{Figures/8}};
   % \node[anchor=south west, inner sep=0] at (0,-11.25){\includegraphics[width=.5\columnwidth]{Figures/9}};
    %\node[anchor=south west, inner sep=0] at (8,-11.25){\includegraphics[width=.5\columnwidth]{Figures/10}};
    %\node[anchor=south west, inner sep=0] at (0,-15){\includegraphics[width=.5\columnwidth]{Figures/11}};
    %\node[anchor=south west, inner sep=0] at (8,-15){\includegraphics[width=.5\columnwidth]{Figures/13}};
